---
title: "Assignment 5: Under (blood) pressure"
author: Sangwon Yum
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(modelr))
# Load dataset
blood_pressure <- read_rds("blood_pressure.rds")
```

## Exercise 1

```{r, fig.asp= 1, fig.width = 8, out.width = "100%"}
blood_pressure %>%
  pivot_longer(cols = Age:Pulse, names_to = "measurement", values_to = "value") %>%
  ggplot() +
    geom_point(mapping = aes(x = value, y = Systol)) +
    facet_wrap(~ measurement, scales = "free_x") +
    geom_smooth(mapping = aes(x = value, y = Systol), method = "lm")
```

## Exercise 2

- Q) What type of correlation does the "Years"
variable demonstrate with "Systol"?
  - Positive?
  - Negative?
  - None?
- A) Negative (-0.087)

- Q) Which variable shows a moderate-to-strong positive correlation with 
"Systol"?
- A) Weight (0.521)

```{r, fig.asp= 1, fig.width = 8, out.width = "100%"}
blood_pressure %>%
  pivot_longer(cols = Age:Pulse, names_to = "measurement", values_to = "value") %>%
  ggplot() +
    geom_point(mapping = aes(x = value, y = Systol)) +
    facet_wrap(~ measurement, scales = "free_x") +
    geom_smooth(mapping = aes(x = value, y = Systol), method = "lm")

# correlation coefficient
cor(blood_pressure)[ ,1]
```

## Exercise 3

```{r}
blood_pressure_updated = blood_pressure %>%
  mutate(
    urban_frac_life = Years / Age
    )
```

## Exercise 4

```{r}
systol_urban_frac_model = lm(Systol ~ urban_frac_life, data
                             = blood_pressure_updated)
```

## Exercise 5

```{r}
systol_urban_frac_model %>% 
  tidy()

model_performance = glance(systol_urban_frac_model)
print(model_performance[, 1:3])
```

## Exercise 6

- Q) What is the name of the column that holds the response variable values 
predicted by the model?
- A) pred

- Q) What is the name of the column that holds the residuals for each 
observation?
- A) resid

```{r}
systol_urban_frac_df = blood_pressure_updated %>% 
  add_predictions(systol_urban_frac_model) %>% 
  add_residuals(systol_urban_frac_model)

print(systol_urban_frac_df)
```

## Exercise 7

- Q) Does your model meet the linearity condition?
- A) It is distributed symmetrically and evenly based on the red line, 
satisfying linearity.
```{r}
ggplot(systol_urban_frac_df) +
  geom_point(mapping = aes(x = pred, y = Systol)) +
  geom_abline(intercept=0, slope=1, color="red") +
   labs(title="Actual vs Predicted", x="Predicted", y="Actual")
```

## Exercise 8

- Q) Does it look like the variability is reasonably constant all the way along
the line?
- A) Since it is evenly distributed based on the red line, the volatility of the
residuals is constant.

- Q) Does the model meet the third criteria of constant variability of 
residuals?
- A) Same as previous answer.
```{r}
ggplot(systol_urban_frac_df, aes(x=pred, y=resid)) + 
  geom_point() + 
  geom_hline(yintercept = 0, color = "red") + 
  labs(title="Residuals vs Predicted", x="Predicted", y="Residuals")
```

## Exercise 9

What is the shape of the distribution of the residuals?
- Q) Symmetric?
- A) Symmetry

- Q) Skewed?
- A) tilted to the right

- Q) Does the model seem to meet the second condition of nearly normal 
residuals? Why or why not?
- A) In the residual histogram, it is judged to be a normal residual because 
it is normally distributed with 0 as the standard.

```{r}
ggplot(systol_urban_frac_df, aes(x=resid)) +
  geom_histogram(binwidth=25) +
  labs(title="Histogram of Residuals", x="Residuals", y="Frequency")
```

## Exercise 10

- Q) Does this new model perform better or worse than the previous model?
- A) The coefficient of determination of the new linear model 
(systol_weight_model) is 0.27, showing better prediction performance than the 
existing linear model (systol_urban_frac_model, coefficient of determination 
= 0.07).

```{r}
systol_weight_model = lm(Systol ~ Weight, data = blood_pressure_updated)

systol_weight_model %>% 
  tidy()

systol_weight_model %>% 
  glance()
```

## Exercise 11

- Q) Does this model and the visualizations created from it follow the 
assumptions necessary for a linear model?
- A) It is distributed symmetrically and evenly based on the red line,
satisfying linearity.

- Q) Does the model meet the third criteria of constant variability of 
residuals?
- A) Same as previous answer

Should we conclude that the second model is reliable? Why or why not?
- Q) Symmetric?
- A) Symmetry

- Q) Skewed?
- A) tilted to the left

- Q) Does the model seem to meet the second condition of nearly normal 
residuals? Why or why not?
- A) In the residual histogram, it is judged to be a normal residual because 
it is normally distributed with 0 as the standard.

```{r}
# Exercise 06
systol_weight_df = blood_pressure_updated %>% 
  add_predictions(systol_weight_model) %>% 
  add_residuals(systol_weight_model)
print(systol_weight_df)

# Exercise 07
ggplot(systol_weight_df) +
  geom_point(mapping = aes(x = pred, y = Systol)) +
  geom_abline(intercept=0, slope=1, color="red") +
  labs(title="Actual vs Predicted", x="Predicted", y="Actual")

# Exercise 09
ggplot(systol_weight_df, aes(x=resid)) +
  geom_histogram(binwidth=25) +
  labs(title="Histogram of Residuals", x="Residuals", y="Frequency")
```

## Exercise 12

+ How does the second model compare with the first in terms of
- Q) Their R2 values
- A) The modified coefficient of determination of the new linear model 
(systol_weight_model) is 0.27, showing better prediction performance than the 
existing linear model (model_performance, coefficient of determination = 0.07).

- Q) How well they meet the 3 assumptions
- A) New/existing linear models are judged by linearity and normal residuals.

```{r}
summary(systol_urban_frac_model)
summary(systol_weight_model)
```
