---
title: "Lab 10: Predicting house prices"
author: "Sangwon Yum"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    highlight: tango
    toc: false
    df_print: kable
    fig_caption: no
    number_sections: no
    dev: pdf
    latex_engine: xelatex
mainfont: "Malgun Gothic"
---

```{r setup, include = FALSE}
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE, fig.width = 6, warning = FALSE,
  message = FALSE, fig.asp = 0.618, out.width = "80%", dpi = 120,
  fig.align = "center", cache = FALSE
)

# is_pdf <- try (("pdf_document" %in% rmarkdown::all_output_formats(knitr::current_input())), silent=TRUE)
# is_pdf <- (is_pdf == TRUE)

# Load required packages
suppressPackageStartupMessages(library(tidyverse, quietly = TRUE))
suppressPackageStartupMessages(library(modelr))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(lmvar))
suppressPackageStartupMessages(library(remotes))
# install.packages("remotes") require(remotes)
# install.packages("lmvar", version = "1.5.2", repos = "http://cran.us.r-project.org")
# install.packages(c("maxLik", "matrixcalc"))
# install.packages("https://cran.r-project.org/src/contrib/Archive/lmvar/lmvar_1.5.2.tar.gz", repos = NULL, type="source")

# Load dataset
train = read_csv("housing_train.csv")
test = read_csv("housing_test.csv")
```

## Exercises
#### Exercise 1
- Q) What are the cities with a high density of houses?
- A) Southren California
```{r, warning=FALSE}
ggplot(train, aes(x = longitude, y = latitude)) + 
  geom_point(alpha = 0.1) +
  labs(title = "Scatter Plot of Housing Locations in California", 
       x = "Longitude", 
       y = "Latitude")
```

#### Exercise 2
- Q) Around what cities do most of the high house values seem to be located in California?
- A) Southren California
```{r, warning=FALSE}
ggplot(train, aes(x = longitude, y = latitude, color = median_house_value)) +
  geom_point(alpha = 0.5) +  
  scale_color_gradient(low = "white", high = "blue") + 
  labs(title = "California Home Values by Location",
       x = "Longitude",
       y = "Latitude",
       color = "Median House Value")
```

#### Exercise 3
- Q) Which variable has the most obvious relationship with median_house_value?
- A) median_income의 경우 선형 관계뿐만 아니라 상관계수 0.69임
- Q) What is the maximum value for the response variable? Why will this maximum limit cause problems for making predictions with a linear model?
- A) median_house_value에서 500,001 최대값을 보이고 너무 높은 이상치일 경우 예측 적합성이 낮을 수 있음
```{r, warning=FALSE}

trainL1 = train %>%
  pivot_longer(cols = housing_median_age:median_income, 
               names_to = "variable", 
               values_to = "value")

ggplot(trainL1, aes(x = value, y = median_house_value)) +
  geom_point(aes(color = value), alpha = 0.1) +
  facet_wrap(~ variable, scales = "free") +
  labs(title = "Relationship with Median House Value",
       x = "Variable Value",
       y = "Median House Value")

cor(train %>% dplyr::select(housing_median_age:median_income, "median_house_value"))

maxVal = max(train$median_house_value, na.rm = TRUE)
print(maxVal)
```


#### Exericse 4
- Q) Which category of houses have the lowest median prices?
- A) INLAND
```{r, warning=FALSE}
ggplot(train, aes(x = ocean_proximity, y = median_house_value)) + 
  geom_boxplot() +
  labs(title = "Box Plot of House Prices by Ocean Proximity",
       x = "Ocean Proximity",
       y = "House Price")

train %>%
  group_by(ocean_proximity) %>%
  summarize(medianVal = median(median_house_value)) %>%
  arrange(medianVal)
```

#### Exericse 5
- Q) What is the RMSE of this model?
- A) 83562.86
```{r, warning=FALSE}
model_1 = lm(median_house_value ~ median_income, data = train, x = TRUE, y = TRUE)

model_1_cv = lmvar::cv.lm(model_1, k = 10)
print(model_1_cv$MSE_sqrt$mean)
```

#### Exericse 6
- Q) Which model performs best?
- A) 68645.03
```{r, warning=FALSE}
model_2 = lm(median_house_value ~ ., data = train, x = TRUE, y = TRUE)

model_2_cv = lmvar::cv.lm(model_2, k = 10)
print(model_2_cv$MSE_sqrt$mean)
```

#### Exericse 7
- Q) What is the root mean square error of this model on the test data?
- A) 모델1 (84317.11), 모델2 (69274.46)
- Q) Is that better or worse than the error in cross-validation?
- A) 교차검증 결과에 비해 높은 오차를 보임 (worse)
```{r, warning=FALSE}
model_1_prd = predict(model_1, newdata = test)
model_2_prd = predict(model_2, newdata = test)

print(sqrt(mean((test$median_house_value - model_1_prd)^2, na.rm = TRUE)))
print(sqrt(mean((test$median_house_value - model_2_prd)^2, na.rm = TRUE)))

```