---
title: "Lab 5: Data cleaning"
author: Sangwon Yum
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
    latex_engine: xelatex
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
    latex_engine: xelatex
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  cache = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 5,
  fig.asp = 0.618,
  fig.align = "center",
  out.width = "80%",
  dpi = 120
)
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(lubridate))
# Load dataset
towed <- read_rds("towed_vehicles.rds")
```


## Exercises
### Exercise 1
```{r, warning=FALSE}
towed_renamed = towed %>% 
  rename_all(~ str_to_lower(.) %>%
               str_replace_all(pattern = "\\s+", replacement = "_"))
print(colnames(towed))
print(colnames(towed_renamed))
```



### Exercise 2
```{r, warning=FALSE}
towed_renamed_2 = towed_renamed %>% 
  mutate(tow_date = mdy(tow_date))
str(towed_renamed_2)


tow_make_count = towed_renamed_2 %>%
  count(make) %>%
  arrange(n)
```

### Exercise 3
- Q) Number of unique values
- A) 78

- Q) Number of values with a count of 1
- A) 28
```{r, warning=FALSE}
unique_cnt = towed_renamed_2 %>%
  summarise(unique_values = n_distinct(make))
print(unique_cnt)

first_cnt <- tow_make_count %>%
  filter(n == 1) %>%
  nrow()
print(first_cnt)
```


### Exercise 4
```{r, warning=FALSE}
slice_function = function(data, i = 1) {
  inv = 10
  start = (i - 1) * inv + 1
  end = i * inv
  
  dataL1 = data %>%
    slice(start:end)
  
  makePlot = ggplot(data = dataL1) +
    geom_col(mapping = aes(x = fct_rev(make), y = n)) +
    coord_flip() +
    labs(title = paste("Make Count for Rows", start, "to", end)) +
    xlab("Make") +
    ylab("count")
    
  print(makePlot)
  
  return(dataL1)
}
```



### Exercise 5

```{r, warning=FALSE}
tow_make_count_1 = slice_function(tow_make_count, 1)
tow_make_count_2 = slice_function(tow_make_count, 2)
tow_make_count_3 = slice_function(tow_make_count, 3)
tow_make_count_4 = slice_function(tow_make_count, 4)


# towed_renamed_2 %>% 
  # mutate(make = recode(make, DODD = "DONG"))

# towed_renamed_2 %>% 
#   mutate(
#     make = recode(
#       make
#       , MISPELLED1 = "CORRECTED1"
#       , MISPELLED2 = "CORRECTED2"
#       , MISPELLED3 = "CORRECTED3"
#       )
#     )
```


### Exercise 6
```{r, warning=FALSE}
towed_partial_clean = towed_renamed_2 %>% 
  mutate(
    make = recode(
      make
      , DODD = "DODG"
      , BUCI = "BUIC"
      )
    )
print(towed_partial_clean)
```



### Exercise 7
- Q) Is it "JAG" or "JAGU"
- A) JAGU

### Exercise 8
```{r, warning=FALSE}
towed_make_clean = towed_partial_clean %>% 
  mutate(
    make = recode(
      make
      , JAG = "JAGU"
      , DODD = "DODG"
      , BUCI = "BUIC"
      )
    )
print(towed_make_clean)
```

## Additional questions
### Question 1
- Q) which make of automobile was impounded the most often in this dataset?
- A) CHEV

```{r, warning=FALSE}
most_impounded_make <- towed_make_clean %>%
  count(make) %>%
  arrange(-n) %>%
  head(1)

print(most_impounded_make)
```


### Question 2
- Q) which make of automobile was impounded the most often in this dataset?
- A) 2018-03-04	

- Q) which day had the most cars impounded? which day had the least cars impounded?
- A) 2018-03-01	
```{r, warning=FALSE}
daily_impounds = towed_make_clean %>%
  count(tow_date) %>%
  arrange(-n)

most_impounded_day = head(daily_impounds, 1)
print(most_impounded_day)

least_impounded_day = tail(daily_impounds, 1)
print(least_impounded_day)
```