---
title: "Assignment 6: Who busts the Mythbusters?"
author: "Sangwon Yum"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    highlight: tango
    toc: false
    df_print: kable
    fig_caption: no
    number_sections: no
    dev: pdf
    latex_engine: xelatex
  html_document:
    highlight: tango
    self_contained: true
    theme: paper
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: no
    smart: yes
    dev: svg
  github_document:
    html_preview: false
    pandoc_args: --webtex
    toc: true
    toc_depth: 4
    dev: svg
    df_print: kable
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)

# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(infer))
set.seed(42)

# Load dataset
experimental_data <- read_csv("yawn.csv")
```

---


### Exercise 1
- Q) Which variable is the response variable and which is the explanatory variable?
- A) 반응 변수 (yawn), 설명변수 (group)

- Q) What value in the response variable is classified as a success?
- A) 반응 변수 (yawn)에서 success (yes)
```{r, warning=FALSE}
summary(experimental_data)
```  


## Exercise 2
- Q) Choose one of the four answer options for should be used to build the null distribution
- A) 4번


## Exercise 3
```r
specify(response = yawn, explanatory = group, success = "yes")
```

## Exercise 4

```r
hypothesize(null = "independence")
```

## Exercise 5

```r
generate(reps = 10000, type = "permute")
```

## Exercise 6

```r
calculate(stat = "diff in props", order = c("Treatment", "Control"))
```

## Exercise 7
```{r, warning=FALSE}
set.seed(50)

yawn_null = experimental_data %>% 
  specify(response = yawn, explanatory = group, success = "yes") %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in props", order = c("Treatment", "Control"))

print(yawn_null)
```



## Exercise 8
```{r, warning=FALSE}
# The histogram
ggplot(yawn_null, aes(x = stat)) +
  geom_histogram(binwidth = 0.1) +
  labs(title = "Null Distribution of Difference in Proportions",
       x = "Difference in Proportions",
       y = "Count")

# The first density plot
ggplot(yawn_null, aes(x = stat)) +
  geom_density(fill = "grey", alpha = 0.5) +
  labs(title = "Density Plot of Difference in Proportions",
       x = "Difference in Proportions",
       y = "Density")

# The second density plot
ggplot(yawn_null, aes(x = stat)) +
  geom_density(adjust = 5, fill = "grey", alpha = 0.5) +
  labs(title = "Adjusted Density Plot of Difference in Proportions",
       x = "Difference in Proportions",
       y = "Density")
```




## Exercise 9
```{r, warning=FALSE}
ggplot(yawn_null, aes(x = stat)) +
  geom_histogram(aes(y = ..density..), binwidth = 0.1, fill = "blue",  alpha = 0.4) +
  geom_density(alpha = 0.2, fill = "#FF6666") +
  labs(title = "Null Distribution with Histogram and Density Plot",
       x = "Difference in Proportions",
       y = "Density") 
```

## Exercise 10
```{r, warning=FALSE}
yawn_null_pmf = yawn_null %>%
  group_by(stat) %>%
  summarise(prob = n() / sum(n()))
print(yawn_null_pmf)

ggplot() +
  geom_col(data = yawn_null_pmf, aes(x = stat, y = prob), binwidth = 0.1, alpha = 0.5) +
  geom_density(data = yawn_null, aes(x = stat, y = ..scaled..), color = "red") +
  labs(x = "Difference in Proportions", y = "Probability") +
  theme_minimal()
```

## Exercise 11
-	Q) Is there sufficient evidence to reject the null hypothesis?
- A) p-value가 0.5094로서 0.05 이상이기 때문에 통계적으로 유의하지 않음 (우연에 의해 발생할 가능성 높음). 즉 null 가설을 기각할 수 없기에 하품의 빈도는 treatment의 영향을 받지 않음

-	Q) Explain why using examples from the previous exercises
- A) 연습 8~10의 경우 히스토그램 및 밀도그램을 통해 두 그룹에서의 하품 비율 차이의 분포를 정성적으로 비교 분석함. 반면에 연습 11에서는 정량적으로 유의수준 (p-value)를 통해 비교 분석함.
```{r, warning=FALSE}
yawn_obs_stat = experimental_data %>%
  specify(response = yawn, explanatory = group, success = "yes") %>%
  calculate(stat = "diff in props", order = c("Treatment", "Control"))
print(yawn_obs_stat)

p_value = yawn_null %>%
  get_p_value(obs_stat = yawn_obs_stat, direction = "greater")
print(p_value)

yawn_null %>%
  visualize() +
  shade_p_value(obs_stat = yawn_obs_stat, direction = "greater") +
  labs(title = "Distribution of Null Hypothesis with Observed Statistic",
       x = "Difference in Proportions",
       y = "Density")

```
