---
title: "GSE_BigData_Prediction_Assignment1"
author: "Add your name"
date: "`r Sys.Date()`"
output: word_document
---

## Set the working directory and read in the dataset (`PISA2018MS_KOR_BQ.rdata`)

```{r readin}
# working directory path를 지정하고 dataset을 넣은 뒤, 아래 세 라인의 #를 지우고 activate해 주세요.
infile <- outfile <-  getwd()
setwd(infile)
load("PISA2018MS_KOR_BQ.rdata")
```

## Prediction task using the linear regression

### Check the dimension of the dataset
```{r dim}
dim(PISA2018MS_KOR)

```

### Compute the mean and sd of PV1MATH variable (outcome variable)
```{r outcome}
mean(PISA2018MS_KOR$PV1MATH, na.rm = TRUE)
sd(PISA2018MS_KOR$PV1MATH, na.rm = TRUE)
```

### Fit the following three prediction models and return the summary of each model: 
* M1: PV1MATH by EMOSUPS
* M2: PV1MATH by explanatory variable: EMOSUPS,  ST004D01T (gender)
* M3: PV1MATH by explanatory variables: EMOSUPS, ST004D01T (gender), interaction between EMOSUPS and ST004D01T (gender)
```{r linear_reg}
M1 = lm(PV1MATH ~ EMOSUPS, data = PISA2018MS_KOR)
summary(M1)


PISA2018MS_KOR2 = PISA2018MS_KOR

M2 = lm(PV1MATH ~ EMOSUPS + ST004D01T, data = PISA2018MS_KOR)
summary(M2)

M3 = lm(PV1MATH ~ EMOSUPS + ST004D01T + EMOSUPS * ST004D01T, data = PISA2018MS_KOR)
summary(M3)

```

### Interpret the coefficients of M2 and M3
#### M2 계수 추정치 해석
* 절편 (intercept) 추정치 = 522.432: EMOSUPS가 0일 때 여학생들의 평균 수학 점수가 522.432
* ST004D01T 추정치 =  : 
* EMOSUPS 추정치 = : 

#### M3 계수 추정치 해석
* 절편 (intercept) 추정치 = 522.544: EMOSUPS가 0일 때 여학생들의 평균 수학 점수가 522.544
* ST004D01T 추정치 =  :
* EMOSUPS 추정치 =  :
* as.factor(ST004D01T) =   :   
* 상호작용 효과가 ~~ 하므로, ~~다고 결론내릴 수 있음

# Check the assumptions of M2 using the `plot` function
```{r assumption}
plot(M2)

```

