---
title: "GSE_BigData_Classification_Assignment3"
author: "Add your name"
date: "`r Sys.Date()`"
output: word_document
---

### Set the working directory and read in the dataset (`PISA2018MS_KOR_BQ.rdata`)

```{r readin}
infile <- outfile <-  ""
# setwd(infile)
getwd()
# load("")
```

### Classification using the logistic regression

#### Make the table of the outcome variable `EC154Q02IA`
* EC154Q02IA: attending additional instruction in mathematics
* Make sure to to include if there are any missing cases (`useNA='always'`)

```{r NAcheck}

```

#### Treatment of outcome variable
* Remove the missing cases of the outcome variable 
* Check the dimension
* Recode 1 -> 0 & 2 -> 1
* Create the table again to check if the recoding is done successfully
```{r outcome}


```

###  Three ways to compute proportions: outcome variable by gender 
#### Create three types of tables 
```{r proportions}




```

#### Interpret the proportions of each table

* Out of total observations, 
* Among the students who do not attend additional instruction in math (conditional on math == 2), 
* Among female students (conditional on gender == 1), 

### Logistic regression
#### Fit the following three logistic regressions (no interpretation is required)
* M1: EC154Q02IA by ST004D01T (gender)
* M2: EC154Q02IA by explanatory variable: PV1MATH,  ST004D01T (gender)
* M3: EC154Q02IA by explanatory variables: PV1MATH, ST004D01T (gender), interaction between PV1MATH and ST004D01T (gender)

```{r assumption}




```

