---
title: "GSE_BigData_Classification_Assignment3"
author: "Add your name"
date: "`r Sys.Date()`"
output: word_document
---

### Set the working directory and read in the dataset (`PISA2018MS_KOR_BQ.rdata`)

```{r readin}
# infile <- outfile <-  ""
# setwd(infile)
# getwd()
# load("")

infile <- outfile <-  getwd()
setwd(infile)
load("PISA2018MS_KOR_BQ.rdata")

data = PISA2018MS_KOR[ , c("PV1MATH", "EMOSUPS", "ST004D01T", "EC154Q02IA")]
```

### Classification using the logistic regression

#### Make the table of the outcome variable `EC154Q02IA`
* EC154Q02IA: attending additional instruction in mathematics
* Make sure to to include if there are any missing cases (`useNA='always'`)

```{r NAcheck}
table(data$EC154Q02IA, useNA='always')
```

#### Treatment of outcome variable
* Remove the missing cases of the outcome variable 
* Check the dimension
* Recode 1 -> 0 & 2 -> 1
* Create the table again to check if the recoding is done successfully
```{r outcome}
dataL1 = subset(data, ! is.na(EC154Q02IA))
dim(data)

# Recode
dataL1$EC154Q02IA[dataL1$EC154Q02IA == 1] = 0
dataL1$EC154Q02IA[dataL1$EC154Q02IA == 2] = 1

# Check recoding
table(dataL1$EC154Q02IA, useNA='always')

```

###  Three ways to compute proportions: outcome variable by gender 
#### Create three types of tables 
```{r proportions}
# 전체
prop.table(table(dataL1$EC154Q02IA))

# 남성
prop.table(table(dataL1$EC154Q02IA[dataL1$ST004D01T == 2]))

# 여성
prop.table(table(dataL1$EC154Q02IA[dataL1$ST004D01T == 1]))
```

#### Interpret the proportions of each table

* Out of total observations, 
* Among the students who do not attend additional instruction in math (conditional on math == 2), 
* Among female students (conditional on gender == 1), 

### Logistic regression
#### Fit the following three logistic regressions (no interpretation is required)
* M1: EC154Q02IA by ST004D01T (gender)
* M2: EC154Q02IA by explanatory variable: PV1MATH,  ST004D01T (gender)
* M3: EC154Q02IA by explanatory variables: PV1MATH, ST004D01T (gender), interaction between PV1MATH and ST004D01T (gender)

```{r assumption}
dataL2 = subset(dataL1, ST004D01T == 1)

M1 = glm(EC154Q02IA ~ ST004D01T, data=dataL2, family=binomial())
M2 = glm(EC154Q02IA ~ PV1MATH + ST004D01T, data=dataL2, family=binomial())
M3 = glm(EC154Q02IA ~ PV1MATH + ST004D01T + PV1MATH * ST004D01T, data=dataL2, family=binomial())
```



### [EXTRA] Model Evaluation 
#### Predict the probabilities and values (either 0 or 1) from each model
* Keep `get_logistic_pred` function 
* You need to generate three sets of predicted values based on each model (M1, M2, M3)
```{r logit_pred}
get_logistic_pred = function(mod, data, res = "y", pos = 1, neg = 0, cut = 0.5) {
  probs = predict(mod, newdata = data, type = "response")
  ifelse(probs >= cut, pos, neg)
}

dataL2$prdM1 = get_logistic_pred(M1, dataL2)
dataL2$prdM2 = get_logistic_pred(M2, dataL2)
dataL2$prdM3 = get_logistic_pred(M3, dataL2)
```

#### Evaluate models (M2 & M3) based on the following quantities
* Report Accuracy, Specificity, Subjectivity, F1 score from M2 & M3
* Use `confusion matrix`
```{r confmat}
library(caret)

confusionMatrix(as.factor(dataL2$prdM2), as.factor(dataL2$EC154Q02IA))
confusionMatrix(as.factor(dataL2$prdM3), as.factor(dataL2$EC154Q02IA))

```