---
title: "Assignment 4: Capital Bikeshare"
author: "Sangwon Yum"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE, echo=FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)

# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(lubridate))
suppressPackageStartupMessages(library(geosphere))
bikeshare <- readRDS("bikeshare_data.RDS")
```

## Exercise 1
i. Identify two continuous variables in this dataset.
```{r, warning=FALSE}
# start_lat, start_lng, end_lat, end_lng
bikeshare %>%
   dplyr::select(
     start_lat, start_lng, end_lat, end_lng
   ) %>%
  print()
  #View()
```
ii. Identify two categorical variables in this dataset. 
```{r, warning=FALSE}
# rideable_type and member_casual
bikeshare %>%
   dplyr::select(
     rideable_type, member_casual
   ) %>%
  print()
  #View()
```

iii. What does each row in the dataset represent?
```{r, warning=FALSE}
#  [1] "ride_id"            "rideable_type"      "started_at"         "ended_at"          
#  [5] "start_station_name" "start_station_id"   "end_station_name"   "end_station_id"    
#  [9] "start_lat"          "start_lng"          "end_lat"            "end_lng"           
# [13] "member_casual"  
bikeshare %>%
  colnames() %>%
  print()
  #View()
```
## Exercise 2
```{r, warning=FALSE}
bikeshareL1 <- bikeshare %>%
   mutate(
     # duration = ended_at - started_at
     duration = difftime(ended_at, started_at, units = "hours")
   ) 
```
## Exercise 3
```{r}
bikeshareL1 %>%
  ggplot() +
  geom_histogram(mapping = aes(x = duration)) +
  labs(title = "Histogram of Bike Usage Duration", x = "Duration (hours)")
```
i. Describe the center, shape and modality of the histogram +
```{r}
bikeshareL1 %>%
  ggplot() +
  geom_boxplot(mapping = aes(x = duration)) +
  labs(title = "Boxplot of Bike Usage Duration", x = "Duration (hours)")
```
ii. Describe the center and skewness of the boxplot using the template provided
+
```{r}
bikeshareL1 %>%
  ggplot() +
  geom_violin(mapping = aes(x = duration, y = "")) +
  labs(title = "Violin Plot of Bike Usage Duration", x = "Duration (hours)")
```
iii. Describe the shape and center of the plot +
iv. Cannot be described as a violin or stringray +
## Exercise 4
```{r}
bikeshare = bikeshareL1 %>% 
  dplyr::mutate(
    min_distance = distHaversine(cbind(start_lng, start_lat), cbind(end_lng, end_lat))
  )
```

## Exercise 5
```{r}
bikeshare %>%
  ggplot() +
  geom_histogram(mapping = aes(x = min_distance)) +
  labs(title = "Histogram of Bike Usage Min distance", x = "Min distance (meters)")
```

```{r}
bikeshare %>%
  ggplot() +
  geom_boxplot(mapping = aes(x = min_distance)) +
  labs(title = "Boxplot of Bike Usage Min distance", x = "Min distance (meters)")
```

```{r}
bikeshare %>%
  ggplot() +
  geom_violin(mapping = aes(x = min_distance, y = "")) +
  labs(title = "Violin Plot of Bike Usage Min distance", x = "Min distance (meters)")
```

## Exercise 6
```{r}
bikeshare %>%
  ggplot(aes(x = duration, y = min_distance)) +
  geom_point() +
  labs(title = "Scatterplot of Duration vs. Min Distance", x = "Duration", 
       y = "Min Distance (meters)")
```
```{r}
bikeshare %>%
  ggplot(aes(x = duration, y = min_distance)) +
  geom_point(alpha = 0.5) +  # Adjust alpha for transparency, value can be between 0 and 1.
  labs(title = "Scatterplot of Duration vs. Min Distance with Alpha", 
       x = "Duration", y = "Min Distance (meters)")
```

```{r}
bikeshare %>%
  ggplot(aes(x = duration, y = min_distance)) +
  geom_bin2d() +
  labs(title = "Heatmap of Duration vs. Min Distance", x = "Duration", 
       y = "Min Distance (meters)") +
  scale_fill_viridis_c(trans = "log")
```

```{r}
bikeshare %>%
  mutate(
    log_duration = log(as.numeric(duration, units = "hours"))
    , log_min_distance = log(as.numeric(min_distance))
    ) %>% 
  ggplot(aes(x = log_duration, y = log_min_distance)) +
  geom_point() +
  labs(title = "Scatterplot with Log Scaled Axes", x = "Log(Duration)", 
       y = "Log(Min Distance)")
```


## Exercise 7
```{r}
bikeshare %>% 
  dplyr::summarise(
    mean = mean(duration, na.rm = TRUE)
    , median = median(duration, na.rm = TRUE)
    , sd = sd(duration, na.rm = TRUE)
    , skewness = moments::skewness(duration, na.rm = TRUE)
    , min = min(duration, na.rm = TRUE)
    , max = max(duration, na.rm = TRUE)
    , n = n()
  )
```

+ Which group of bike riders has the longest average ride length? casual
+ Did you expect this pattern of casual vs member riders's duration of bike rides?

+ Calculate the number of rides (cnt) for members and regular riders.
+ Which group of riders has done the most riding? member
```{r}  
bikeshare %>%
  dplyr::group_by(member_casual) %>% 
  dplyr::summarise(
    mean = mean(duration, na.rm = TRUE)
    , median = median(duration, na.rm = TRUE)
    , sd = sd(duration, na.rm = TRUE)
    , min = min(duration, na.rm = TRUE)
    , max = max(duration, na.rm = TRUE)
    , n = n()
  )
```

## Exercise 8
```{r}
bikeshare %>%
  ggplot(aes(x = duration, fill = member_casual)) +
  geom_histogram(position = "identity", alpha = 0.3, bins = 20) +
  labs(title = "Distribution of Riding Time by Rider Type", x = "Duration (hours)")
```

```{r}
bikeshare %>%
  ggplot(aes(x = member_casual, y = duration)) +
  geom_violin() +
  labs(title = "Distribution of Riding Time by Rider Type", x = "Rider Type", 
       y = "Duration (hours)")
```

ii. Describe the center and skewness of the boxplot using the template provided
+
```{r}
bikeshare %>%
  ggplot(aes(x = duration, y = min_distance)) +
  geom_bin2d() + 
  facet_wrap(~ member_casual) +
  labs(title = "Heatmap of Duration vs. Min Distance by Rider Type", 
       x = "Duration (hours)", y = "Min Distance") +
  scale_fill_viridis_c(trans = "log")
```


## Exercise 9

+ In order to understand the relationship between driving time (duration) and minimum distance (min_distance), a scatter plot is visualized and analyzed in terms of centrality, relationship, variance, and covariance.

+ (Centrality) Most members are concentrated in areas that cover a short distance within a short period of time. This means that many users prefer short trips.

+ (Relationship) Shows positive correlation between minimum distances depending on driving time.

+ (Dispersion) There is wide dispersion in travel times and minimum distances, resulting in varying user behavior. In particular, members use bicycles consistently by paying a certain fee for quick commuting, while casual users are general users who use bicycles for leisure activities or short-term travel purposes.

+ (Covariance) As in the previous variance, it shows a relationship that gradually increases from the bottom left to the top right (minimum distance according to driving time), which means there is positive covariance.
```{r}
bikeshare %>%
  ggplot(aes(x = duration, y = min_distance, color = member_casual)) +
  geom_point(alpha = 0.5, position = "jitter") +
  labs(title = "Scatterplot of Duration vs. Min Distance", x = "Duration", y = "Min Distance")
```