---
title: "Assignment 3: Flights of New York"
author: Sangwon Yum
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: tibble
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: tibble
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)

# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(nycflights13))
```

## Exercise 1

* How many rows and columns are in the dataset?
  + There are 336776 rows and 19 columns

* What does a single row represent
  + year, month, day, dep_time, sched_dep_time, dep_delay, arr_time, sched_arr_time, arr_delay, 
    carrier, flight, tailnum, origin, dest, air_time, distance, hour, minute, time_hour (show one 
    flight sample)

* What is the difference between arr_time and sched_arr_time?
  + arr_time is the actual arrival time of the plane, and sched_arr_time is the original 
    scheduled arrival time of the plane.

* What variable is the most useful for identifying a specific plane?
  + Flights number is most variable way for identifying a specific plane

## Exercise 2

```{r, warning=FALSE}
flights %>% 
  select(year, month)
```

* Explain the purpose of the select() function based on the output of the code template provided 
  + Replace name of dataset with the variable storing your dataset and column
    
## Exercise 3

```{r, warning=FALSE}
flights %>% 
  select(year:day)
```

* What does using a colon : do?
  + The colon is responsible for showing all information, including the dataset year in 
  parentheses, up to dataset day
    
## Exercise 4

```{r, warning=FALSE}
flights %>%
  arrange(air_time, distance)
```

* Does it look like both air_time and distance were sorted?
  + yes
    
* Which column was sorted with higher priority?
  + year
    
* What would happen if you reverse the order of the variables specified in arrange()?
  + reversed air_time and distance

## Exercise 5

```{r, warning=FALSE}
flights %>%
  arrange(desc(dep_delay))
```

* The longest departure delay flight number is 7073 flight
    
## Exercise 6

```{r, warning=FALSE}
flights %>%
  mutate(
   average_speed = distance / (air_time / 60)
)
```

* Where is the new column located in the output dataframe?
  + last part

* What is the name of the new column?
  + average_speed
  
* Which part of the code determines the name of the new column?
  + average_speed = distance / (air_time / 60)

## Exercise 7

```{r, warning=FALSE}
flights %>%
  mutate(
    dep_time_hour = dep_time %/% 100,
    dep_time_minute = dep_time %% 100,
    dep_time_minutes_midnight = dep_time %% 100
  )
```

## Exercise 8

```{r, warning=FALSE}
flights %>%
  filter(
    arr_delay < 0
  )
```

```{r, warning=FALSE}
flights %>%
  filter(
    carrier == "AA"
  )
```
```{r, warning=FALSE}
flights %>%
  mutate(
    arr_delay < 0,
    carrier == "AA"
  )
```

## Exercise 9

```{r, warning=FALSE}
flights %>%
  group_by(carrier) %>%
  summarize(
    average_arr_delay = mean(arr_delay, na.rm = TRUE)
  )
```
```{r, warning=FALSE}
flights %>%
  group_by(carrier) %>%
  summarize(
    average_departure_delay = mean(dep_delay, na.rm = TRUE)
  )
```
* Which airline carrier had the longest arrival delays on average?
  + F9
  
* Which airline carrier had the shortest arrival delays on average?
  + AS

## Exercise 10

```{r, warning=FALSE}
late_flights_to_miami <- flights %>%
  filter(dest == "MIA")
  select(flights, arr_delay, carrier)
```

## Exercise 11

```{r, warning=FALSE}
monthly_delays <- flights %>%
  group_by(month, carrier) %>%
  summarize(
    arrival_delay = mean(arr_delay, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  pivot_wider(names_from = carrier, values_from = arrival_delay) %>%
  select(-'9E')
```

```{r, warning=FALSE}
# qplot(x = month, y = UA, geom="line", data=monthly_delays)
ggplot(data = monthly_delays, aes(x = month, y = UA)) +
  geom_line() +
  xlab("Month") +
  ylab("UA") +
  ggtitle("Line Graph of UA by Month")  
```

```{r, warning=FALSE}
monthly_delays %>%
  pivot_longer(cols = !month, names_to = "Airline", values_to = "Delays")
```

```{r,warning=FALSE}
prvoted_monthly_delays <- monthly_delays %>%
  pivot_longer(cols = !month, names_to = "Airline", values_to = "Delays")

# qplot(x = month,
#       y = Delays,
#       color = Airline,
#       geom = "line",
#       data = prvoted_monthly_delays
#       )
ggplot(data = prvoted_monthly_delays, aes(x = month, y = Delays, color = Airline)) +
  geom_line() +
  xlab("Month") +
  ylab("Delays") +
  ggtitle("Line Graph of Delays by Month colored by Airline")
```