---
title: 'Assignment 1: R Markdown practice'
author: "Sangwon Yum"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)

# Load required packages
suppressPackageStartupMessages(library(tidyverse))
```

<!-- Write your Markdown below this line -->
#   How the Course Works
Hello World!
```{r, warning=FALSE}
print("Hello World!")
```
# Hello World!
## Hello World!
### Hello World!
#### Hello World!
##### Hello World!
###### Hello World!

The weekly interactive tutorials must be completed by the start of each week. Then each weekly assignment will be due at the end of the week. 

#   Course Goals

By the end of the course, students will be able to 

*   Use [GitHub](https://github.com/23F-CDS-1012/assignment-01-SangwonYum) for creating a reproducible research document. 

    +   My GitHub username is: *SangwonYum* 
  
*   Obtain, clean, transform, and visualize a dataset using the R programming language.

*   Interpret and predict dataset trends using statistical inference and models. 

*   Critically examine and interpret statistical claims reported in mass media. 

#   Including Code

##    Running R code in a code chunk

```{r, warning=FALSE}
x <- 2+2
x + 3
```

The output of first line of code is not printed out because it is assigned to a variable instead. 
The second line of output is printed out instead, but this means that the calculated value has not been saved for future use. 

##    Displaying Graphs

```{r, warning=FALSE}
# ggplot2::qplot(data = iris, x = Sepal.Length, y = Sepal.Width)
ggplot(data = iris, aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_point()
```