---
title: "Assignment 2: Visualization by example"
author: Sangwon Yum
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)

# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(palmerpenguins))
```

## Exercise 1

    i. How many rows and columns does this dataset have?
    
    - 344 rows and 8 columns

    ii. What does a row in this dataset represent?
    
    - species, island, bill length, bill depth, flipper length, body mass, sex, year
    
    iii. What are three categorical variables in the penguins dataset?
    
    - species, island, sex
    
    iv. What are four continuous variables in the penguins dataset? 
    
    - bill length, bill depth, flipper length, body mass
    v. Which variable in the penguins dataset could be treated as either continuous or categorical
    ,depending on the context in which it is used? 
    
    - year
    
    vi. What are the three species of penguin in the dataset?
    
    - Adelie, Gentoo, Chinstrap
    
    
## Exercise 2

```{r, warning=FALSE}
# qplot(x = flipper_length_mm, data = penguins)
ggplot(data = penguins) +
  geom_histogram(mapping = aes(x = flipper_length_mm), binwidth = 5) +
  xlab("Flipper Length (mm)") +
  ylab("Count") +
  ggtitle("Distribution of Flipper Lengths") 
```
    
    i. Which axis of the plot has the flipper variable been plotted on?
    
    - x(flipper_length_mm)
    
    ii. what do the numbers on the other axis of the graph represent?
    
    - penguins
    
    iii. What is the modality of the distribution of flipper lengths?
    
    - Bimodal

## Exercise 3

```{r, warning=FALSE}
# qplot(x = flipper_length_mm, bins = 15, data = penguins)
ggplot(data = penguins) +
  geom_histogram(mapping = aes(x = flipper_length_mm), bins = 15) +
  xlab("Flipper Length (mm)") +
  ylab("Count") +
  ggtitle("Distribution of Flipper Lengths")  
```

    i. Does the distribution in the histogram look more or less noisy than in exercise #02?
    
    - This histogram is less noisy than in exercies #02, because the one of exercise #02 has much 
    more bins. So, it is hard to understand at one glance. 
    
```{r, warning=FALSE}
# qplot(x = flipper_length_mm, binwidth=1, data = penguins)
ggplot(data = penguins) +
  geom_histogram(mapping = aes(x = flipper_length_mm), binwidth = 1) +
  xlab("Flipper Length (mm)") +
  ylab("Count") +
  ggtitle("Distribution of Flipper Lengths")
```

    i. Are there more or fewers bins in the new histogram?
    
    - There are fewer bins in the histogram
    
    ii. Does this increase or decrease the smoothness of the distribution?  
    
    - This increases the smoothness of the distribution
    
    iii. Does that make the pattern of 2 peaks easier or harder to visualize?
    
    - It is easier
    
## Exercise 4

```{r, warning=FALSE}
# qplot(x = flipper_length_mm, y = body_mass_g, data = penguins)
ggplot(data = penguins) +
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g)) +
  xlab("Flipper Length (mm)") +
  ylab("Body Mass (g)") +
  ggtitle("Scatterplot of Body Mass against Flipper Length")
```

    i. What variable is on the y-axis?
    
    - body mass
    
    ii. Is there a relationship between these variables?
    
    - It is linear

## Exercise 5

```{r, warning=FALSE}
# qplot(x = bill_length_mm, y = body_mass_g, data = penguins)
ggplot(data = penguins) +
  geom_point(mapping = aes(x = bill_length_mm, y = body_mass_g)) +
  xlab("Bill Length (mm)") +
  ylab("Body Mass (g)") +
  ggtitle("Scatterplot of Body Mass against Bill Length") 
```

    i. Does the correlation between bill length and body mass look stronger or weaker than the 
    relationship between the variables in exercise #04?
    
    -Unlike the previous scatter plot, this scatter plot does immediately show a weaker 
    correlation between the two variables. 

## Exercise 6

```{r, warning=FALSE}
# qplot(
#   x = flipper_length_mm,
#   y = body_mass_g, 
#   data = penguins, 
#   geom = c("point", "smooth"), 
#   method = "lm")
ggplot(data = penguins) +
  geom_point(mapping = aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_smooth(mapping = aes(x = flipper_length_mm, y = body_mass_g), 
              method = "lm", se = FALSE) +
  xlab("Flipper Length (mm)") +
  ylab("Body Mass (g)") +
  ggtitle("Scatterplot with Linear Regression Line of Body Mass against Flipper Length")
```

    i. Do you think that the patterns this graph make the information more or less clear by showing 
    just the trend line? 
    
    - I thought that this line makes the information more clear because reader can know the trend in 
    few seconds with this line

## Exercise 7

```{r, warning=FALSE}
# qplot(x = bill_length_mm,
#       y = body_mass_g,
#       geom = "point",
#       color = species,
#       data = penguins
#       )
ggplot(data = penguins) +
  geom_point(mapping = aes(x = bill_length_mm, y = body_mass_g, color = species)) +
  xlab("Bill Length (mm)") +
  ylab("Body Mass (g)") +
  ggtitle("Scatterplot of Body Mass against Bill Length colored by Species") 
```

    i. How does coloring the data points of penguin make the relationship between bill length and 
    body mass easier to understand? 
    
    - It is easier, because we can easy to find out which groups have which characteristics