---
title: "Lab 8 - Basketball and Hot Hands"
author: "Sangwon Yum"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    highlight: tango
    toc: false
    df_print: kable
    fig_caption: no
    number_sections: no
    dev: pdf
    latex_engine: xelatex
  html_document:
    highlight: tango
    self_contained: true
    theme: paper
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: no
    smart: yes
    dev: svg
  github_document:
    html_preview: false
    pandoc_args: --webtex
    toc: true
    toc_depth: 4
    dev: svg
    df_print: kable
---

```{r setup, include = FALSE}
# Set knitr options
knitr::opts_chunk$set(
  echo = TRUE, eval = TRUE, fig.width = 6, warning = FALSE,
  message = FALSE,
  fig.asp = 0.618, out.width = "80%", dpi = 120,
  fig.align = "center", cache = FALSE
)

# Load required packages
suppressPackageStartupMessages(library(tidyverse, quietly = TRUE))

# Load the dataset and source function
kobe_basket = read_rds("kobe_basket.rds")

source("calc_streak.R")
```

## Lab report
## Exercises
#### Exercise 1
- Q) How many hits? 
- A) 24

- Q) How many misses?
- A) 52

- Q) Define streak length of zero
- A) 39
```{r, warning=FALSE}
kobe_streack = calc_streak(kobe_basket$shot)
print(kobe_streack)

# 연속 득점 길이가 1인 경우를 필터링
statData = kobe_streack %>% 
  dplyr::group_by(length) %>% 
  dplyr::summarise(
    cnt = n()
  )
print(statData)

# 히트와 미스의 수를 카운트
hitCnt = statData %>% dplyr::filter(length == 1)
print(hitCnt)

misCnt = nrow(kobe_streack) - hitCnt$cnt
print(misCnt)

zeroCnt = statData %>% dplyr::filter(length == 0)
print(zeroCnt)
``` 

#### Exercise 2
- Q) What is the most common streak length?
- A) 0

- Q) What is the longest streak length?
- A) 4
```{r, warning=FALSE}
ggplot(data = kobe_streack) +
  geom_bar(aes(x = length)) +
  labs(title = "Streak Lengths", x = "Length", y = "Frequency")

meanVal = mean(kobe_streack$length, na.rm = TRUE)
cat(sprintf("[CHECK] meanVal : %s", meanVal), "\n")
 
medianVal = median(kobe_streack$length, na.rm = TRUE)
cat(sprintf("[CHECK] medianVal : %s", medianVal), "\n")

# Most common streak length
mostLen = kobe_streack %>%
  group_by(length) %>%
  summarise(cnt = n()) %>%
  arrange(desc(cnt)) %>%
  top_n(1)
cat(sprintf("[CHECK] mostLen : %s", mostLen$length), "\n")

# Longest streak length
maxLen = kobe_streack %>%
  summarise(maxVal = max(length, na.rm = TRUE))
cat(sprintf("[CHECK] maxLen : %s", maxLen), "\n")
```

#### Exercise 3
- Q) Answer how many came up heads
- A) sim_fair_coin: 56, sim_unfair_coin: 17
```{r, warning=FALSE}
set.seed(35797)

coin_outcomes = c("heads", "tails")
# sample(coin_outcomes, size = 1, replace = TRUE)

sim_fair_coin = sample(coin_outcomes, size = 100, replace = TRUE)
print(table(sim_fair_coin))

sim_unfair_coin = sample(coin_outcomes, size = 100, replace = TRUE, prob = c(0.2, 0.8))
print(table(sim_unfair_coin))
```

#### Exericse 4
- Q) sim_basket and kobe_basket both represent the results of 133 shot attempts with the same shooting percentage of 45%
- A) sim_shots: 63, kobe_basket: 58
```{r, warning=FALSE}
set.seed(35797)

shot_outcomes = c("H", "M")

# sim_basket = sample(shot_outcomes, size = 1, replace = TRUE)

shotProb = 0.45
sim_basket = sample(shot_outcomes, size = 133, replace = TRUE, prob = c(shotProb, 1 - shotProb))

sim_basket_shots = sum(sim_basket == "H", na.rm = TRUE)
cat(sprintf("[CHECK] sim_basket_shots : %s", sim_basket_shots), "\n")

kobe_made_shots = sum(kobe_basket$shot == "H", na.rm = TRUE)
cat(sprintf("[CHECK] kobe_made_shots : %s", kobe_made_shots), "\n")
```

## Additional questions
#### Question 1
```{r, warning=FALSE}
sim_streak = calc_streak(sim_basket)
print(sim_streak)
```

#### Question 2
- Q) What is the typical streak length?
- A) 0

- Q) What is the longest streak?
- A) 6
```{r, warning=FALSE}
ggplot(sim_streak, aes(x=length)) +
  geom_bar() +
  labs(title="Streak Lengths of sim_streak", x="Streak Length", y="Frequency")

# Most common streak length
mostLen = sim_streak %>%
  group_by(length) %>%
  summarise(cnt = n()) %>%
  arrange(desc(cnt)) %>%
  top_n(1)
cat(sprintf("[CHECK] mostLen : %s", mostLen$length), "\n")

# Longest streak length
maxLen = sim_streak %>%
  summarise(maxVal = max(length, na.rm = TRUE))
cat(sprintf("[CHECK] maxLen : %s", maxLen), "\n")
```

#### Question 3
- A) 일반적으로 독립적인 슈터 시뮬레이션은 일정한 확률 (성공률 45%, 실패율 55%)로 실행되나 무작위 샘플링의 특성으로 인해 매번 다른 결과를 제공함

#### Question 4
```{r, warning=FALSE}
dataL1 = dplyr::bind_rows(
  dplyr::bind_cols(kobe_streack, name = "kobe")
  , dplyr::bind_cols(sim_streak, name = "sim")
)
print(dataL1)

ggplot(dataL1, aes(x = length, fill = name)) +
  geom_bar(position = "dodge", stat = "count", width = 0.7) +
  labs(title = "Streak Length Distribution of sim_basket vs. kobe_basket", x = "Streak Length", y = "Frequency")
```