---
title: "Assignment 4: Capital Bikeshare"
author: "Sangwon Yum"
date: "`r Sys.Date()`"
documentclass: article
geometry: margin=1in
fontsize: 11pt
output:
  pdf_document:
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    dev: pdf
    highlight: tango
  html_document:
    theme: default
    self_contained: true
    toc: false
    df_print: kable
    fig_caption: false
    number_sections: false
    smart: true
    dev: svg
---

```{r setup, include = FALSE, echo=FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Load required packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(lubridate))
suppressPackageStartupMessages(library(geosphere))
bikeshare <- readRDS("bikeshare_data.RDS")
```


## Exercise 1

i. Identify two continuous variables in this dataset.
+ lat and lng

ii. Identify two categorical variables in this dataset.
+ rideable_type and member_casual

iii. What does each row in the dataset represent?
+ 

## Exercise 2

```{r, warning=FALSE}
bikeshare <- bikeshare %>%
   mutate(
     duration = ended_at - started_at
   )
```


## Exercise 3

```{r}
bikeshare %>%
  ggplot() +
  geom_histogram(mapping = aes(x = ...)) +
  labs(title = "...", x = "...")
```

i. Describe the center, shape and modality of the histogram
+ 

```{r}
... %>%
  ggplot() +
  geom_boxplot(mapping = aes(x = ...)) +
  labs(title = "...", x = "...")
```

ii. Describe the center and skewness of the boxplot using the template provided
+ 

```{r}
... %>%
  ggplot() +
  geom_violin(mapping = aes(x = ..., y = '')) +
  labs(title = "...", x = "...")
```

iii. Describe the shape and center of the plot
+

iv. Cannot be described as a violin or stringray
+ 


## Exercise 4



## Exercise 5



## Exercise 6



## Exercise 7



## Exercise 8



## Exercise 9



